\begin{multicols}{2} 

    \CvSection{Work Experiences}{
        \CvSectionEntry{Jr. R\&D Software Engineer}{
            \textbf{Date:} 07/2018 - 08/2020 (2 year 1 months) \\
            \textbf{Place:} Cantek Group \\
            \textbf{Job Descirption:} \\
            \textbf{-} Using Hybrid Database Architectures with combining \\
            PostgreSQL + Cassandra technologies \\
            \textbf{-} Developing Java Microservices with Spring Boot  \\
            (mostly Spring Framework Core, Spring Security and Spring Cloud Modules)  \\
            and deploying them as a Docker containers on the server \\
            \textbf{-} Using Docker, GitLab, Jenkins, JFrog Artifactory technologies.\\
            \textbf{-} Working on a system which is running on Ubuntu 16.04 server \\
            and apply DevOps by using CI/CD Software that each one is running inside \\
            separate Docker containers. \\
            \textbf{|} Managing source code via GitLab \\
            \textbf{|} Compiling Spring Boot applications with Maven via Jenkins \\
            \textbf{|} Serving JARs on the JFrog Artifactory via Jenkins \\
            \subsubsection*{Software Engineering Internship (2 months)}
            \textbf{-} Research Docker, GitLab, Jenkins, JFrog Artifactory technologies. \\
            \textbf{-} Comparing Project Management Tools (Jira, Trello, Taiga.io, GitLab Tools). \\
            \textbf{-} Running GitLab - Jenkins - JFrog Artifactory in separate Docker containers. \\
            \textbf{-} Setup a system on Ubuntu 16.04 server to \\
            \textbf{|} Managing source code via GitLab \\
            \textbf{|} Compiling Spring Boot applications çwith Maven via Jenkins \\
            \textbf{|} Serving JARs on the JFrog Artifactory via Jenkins \\
        }

        \CvSectionEntry{Java Developer}{
            \textbf{Date:} 06/2016 - 06/2018 (2 year) \\
            \textbf{Place:} Akdeniz University BAUM \\
            \textbf{Job Description:} \\
            \textbf{-} Developing Java Web Apps (Spring MVC) with using Spring framework \\
            \textbf{-} Providing communication between web apps and database \\ 
            over RESTful Service \\
            \textbf{-} Compiling applications with Maven, sending them to the SVN environment, \\ 
            serving them on the Tomcat Server via Jenkins. \\
            \textbf{Volunteer  (2 months)} \\
            \textbf{-} Web page design using the Bootstrap library \\ 
            with HTML5-CSS3-JavaScript for Spring, MVC Web Apps
        }

    }
    

    
    \colbreak
    \CvSection{Freelance Works}{
        \CvSectionEntry{IconConference2017 Website}{
            \textbf{Job Description:} A personal wordpress conference website design
            and web application to upload abstracts developed with PHP    
        }
    }    

    \CvSection{Personal Projects}{
        \CvSectionEntry{Spring VIP}{
            \textbf{Home Page:} https://springvip.yazilim.vip \\
            \textbf{Description:} 
            A Java Spring Library that provides helpful generic and utility classes. Some of features provided by library are generic CRUD Service and Rest controllers. See more from documentation
        }
        
        \CvSectionEntry{maescript}{
            \textbf{Home Page:} https://yazilim-vip.github.io/maescript/ \\
            \textbf{Description:} 
            Very useful set of linux commands
        }
    }    
    
    \CvSection{Attended Organizations}{
        \textbf{UBMK 17: }Crew \\
        \textbf{3. Antalya Bilim Şenliği: }Participant \\
        \textbf{Linux Seminar: }Undergraduate Seminar
    }    

\end{multicols}